HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
appendix C & D

>>>>

\section{Appendix C: Consent Form}
I hereby consent to participate in the research study conducted by Ajit Pawar, Colin White, Ishan Thukral, Kyra Assaad, and Zach Munro-Cape as part of the Fall 2015 semester project for CSC428, Human-Computer Interaction, offered by the Department of Computer Science at the University of Toronto.

I agree to participate in this study whose purpose is to evaluate the accuracy and speed of stacked/unstacked smartphone multitasking interfaces.

I understand that:
\begin{itemize}
\item The study uses direct observation.
\item There are no significant risks incurred by participating in this experiment.
\item I will receive no compensation of my participation.
\item I am free to withdraw at any time during the study without the need to give any explanation or reason and without any penalty.
\item All material and results will be kept confidential, and, in particular, that my name and any identifying or identified information will not be associated with the data.
\item I can contact the course lecturer, Oliver St. Cyr (stcyr@mie.utoronto.ca), with any questions or concerns.
\end{itemize}

\textbf{PARTICIPANT:}\\
Name (please print): \\
Signature:\\
Date:\\

\textbf{INVESTIGATOR:}\\
Name:\\
Signature:\\

\section{Appendix D: Entry Survey}
What is your age? (choose one)\\
* Under 17\\
* 17-23\\
* 24-30\\
* 31-40\\
* 40+

What is your gender? (choose one)\\
* Male\\
* Female\\
* Trans*\\
* Other\\

Are you: (choose one)\\
* Right-handed\\
* Left-handed\\
* Ambidextrous\\

Have you used the Android operating system before? (choose one)\\
* Yes\\
* No\\

Do you own an Android phone? (choose one)\\
* Yes\\
* No\\

What version of Android are you most comfortable with? (choose one)\\
* KitKat\\
* Lollipop\\
* Marshmallow\\
* I’m not sure\\
* Other\\

What model of phone do you have? (write below)\\
